Continuous Generalization of Buildings

### 2017-07-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixed bugs of concerning holes

\title*{Continuous Generalization of Buildings}
\titlerunning{Continuous Generalization of Buildings}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%\author{Dongliang Peng, Alexander Wolff, and Jan-Henrik Haunert}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
% \institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
% \and Name of Second Author \at Name, Address of Institute
% \email{name@email.address}}
\institute{
%	Dongliang Peng 
%	\at Chair of Computer Science I, University of W\"urzburg, 
%	Germany \\
%	\email{dongliang.peng@uni-wuerzburg.de}
%	\and
%	% 
%	Alexander Wolff 
%	\at Chair of Computer Science I, University 
%	of W\"urzburg, Germany \\
%	\url{URL: 
%	
%http://www1.informatik.uni-wuerzburg.de/en/staff/wolff_alexander}
%	\and
%	%
%	Jan-Henrik Haunert 
%	\at Institute for Geoinformatics and Remote Sensing (IGF), 
%	University of Osnabr\"uck, Germany \\
%	\email{janhhaunert@uni-osnabrueck.de}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

When users zoom out on digital maps, buildings become closer with each other 
and buildings themselves become smaller. 
In order to make sure that the map is 
easily perceived \parencite{Weibel1997}, small building should be eliminated, 
some building should be enlarged, and buildings close to each other should be 
aggregated.
Although algorithms of simplifying buildings have been studied, e.g., 
\textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
when we have to aggregate buildings in the meantime.
In order to aggregate, we should first group the buildings.

@@

@@

\subsection{Parameters for growing and simplification}
The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
($S_\mathrm{g}>S_\mathrm{s}$).
The area of a building should be larger than $a$ mm$^2$ on map.
A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm.
Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
In order to eliminate some small buildings, we define our growing distance as
\begin{equation}
\label{eq:d_G}
	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
	the dashed polygon is the enlargement of the building. In the right 
	figure, the dashed polygon has been simplified to a rectangle. In order to 
	fill the rectangle, most parts of the (green) building needs to grow 
	distance $d_\mathrm{G}$, but the pit needs to grow $d_G + d_\mathrm{e}$, 
	where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure}

>>>>

\title*{Continuous Generalization of Buildings}
\titlerunning{Continuous Generalization of Buildings}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Dongliang Peng and Guillaume Touya}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{
	Dongliang Peng 
	\at Chair of Computer Science I, University of W\"urzburg, 
	Germany \\
	\email{dongliang.peng@uni-wuerzburg.de}
	\and
	% 
	Guillaume Touya
	\at COGIT, IGN, France \\
	\email{guillaume.touya@ign.fr}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

When users zoom out on digital maps, buildings become closer with each other 
and buildings themselves become smaller. 
In order to make sure that the map is 
easily perceived \parencite{Weibel1997}, small building should be eliminated, 
some building should be enlarged, and buildings close to each other should be 
aggregated.
Although algorithms of simplifying buildings have been studied, e.g., 
\textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
when we have to aggregate buildings simultaneously.
In order to aggregate, we should first group the buildings.

@@

We grow all the buildings with the same speed.

If several buildings are close to each other at the start 
scale, we bridge them by line segments and take the merge of these 
buildings 
and bridges as one building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the target shape.

@@

\subsection{Parameters for growing and simplifying}
The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
($S_\mathrm{g}>S_\mathrm{s}$).
The area of a building should be larger than $a$ mm$^2$ on map.
A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm.
Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
In order to eliminate some small buildings, we define our growing distance as
\begin{equation}
\label{eq:d_G}
	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
	the gray polygon is the enlargement of the building. In the right 
	figure, the gray polygon has been simplified to a rectangle. In order to 
	fill the rectangle, most parts of the (green) building needs to grow with
	distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
	d_\mathrm{e}$, 
	where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure}
